Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-10-09 tex/main/manuscript.tex
update tables in sup
change abstract and title

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Universal regime transition for water resources utilization in developing river basins}

@@

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{
	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.
	Water, a key resource to support the sustainable development of human societies, whose natural cycle has been modified by growing socio-economic processes. We propose a new method with an integrated index to detect water utilization regimes and applying it to the Yellow River Basin, a typical overexploited basin in China. After sketching changes of relationships between social development and water utilization within the Yellow River Basin, we summarized a universal transition framework. By predicting widespread development dilemmas, it can be a useful guideline for basins all around the world in their sustainable developing trajectories. 
}

@@

%tag 摘要
\begin{abstract}
	From agrarian to industrial societies, humans have harnessed ecosystems over rivers basins around the world, while using water resources as blood that sustains social developments. 
	Although relations between societies and water resources keep changing throughout, there is still lacking effective methods to detect related regimes of water resources utilization, with much fewer attempts to develop theoretical framework to explain their transitions as well. 
	Here, by integrating three important dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts. 
	By applying this index to the Yellow River Basin, China, our results suggest three water utilization regimes in developing over half a century, whose shifts led by various but pervasive causes.
	Based on that, we summarized a universal transition framework which gives a sketch of relationships between human societies and their water utilization, as a useful guideline for big river basins to develop in a coordinated way.
\end{abstract}

@@

% tag 引言第一段
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects. 
% TODO 这里增加三篇“大文章”参引
% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
However, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in various development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% TODO 这里增加参考文献，人类对水循环的改造 
% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need for integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}. 
% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
Therefore, understanding the complex relationship between human societies, water resources utilization and their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.

@@

%tag 结果2
\subsection*{Differences between water utilization regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
The differences between the water utilization regimes are reflected in changes of all three dimensions.
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regimes and their main contributors.
		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		}
	\label{fig:dimensions}
\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).   
% 1. 水资源丰富，耗水量少且灵活用水
In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig. S3) and most of which were flexible water utilization (\textit{SI Appendix} Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix} Fig. S5). As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.

% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts. 
% 首先是用水比例的变化
Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
% 再讨论用水格局的变化
However, configuration of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).

@@

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Drivers of water utilization regime shifts: economy growths, efficiency changes, and management practices.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

@@

\subsection*{Interpret of regime shifts within YRB}
% 我们发明的指数能将三个维度的变化捕捉到。
The IWRU index captures, with three dimensions (stress, priority and configuration), the complex human-water feedbacks that links social development and water resources utilization. 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig. S8). 
% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development then.
% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure (\textit{SI Appendix} Table S2), and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C). 
% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.

% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff. In 1972, the Yellow River was cut off for the first time with a length of 310 km for 19 days, and continued to be cut off for many years since then (\textit{SI Appendix} Fig. S9). 
% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
Came to the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
Since then, the expansion trend of agriculture has been constrained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market. In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 3). For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.

@@

\subsection*{Transition framework of water utilization}

\begin{figure*}[thbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		Transition framework of the water utilization regime towards nature-society dualistic water cycle.
		\textbf{A. Natural cycle:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic cycle, water resource plays a non-provisioning role. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional cycle:} Entering this phase, with further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

@@

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% 资源陷阱和失配，导致崩溃
Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% 转型应对陷阱
A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.

% TODO 这里把图改成全球大河流域的资源问题类型图
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
	\caption{
		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure. Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
	}
	\label{fig:traps}
\end{figure}

% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (Figure~\ref{fig:traps}).
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
In the YRB as an example, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$. The resource dilemma revealed after the regime shift, with severe runoff outages and groundwater depletion of the Yellow River (\textit{SI Appendix} Fig. S8).
% 后来摆脱了资源陷阱（表现形式 xxx）。
To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices. 
% 一段有关87分水方案的介绍
The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}. Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}. 
These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
% 资源困局可能普遍存在
Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource dilemmas is pervasive in the transition trajectory, especially from natural cycle to regional cycle 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
% 通过协同治理来摆脱困局也普遍存在
Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g. Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017,unep-dhiTransboundaryRiverBasins2016}.

>>>>

% PNAS研究论文模板
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
% \usepackage{cite}
\usepackage{url}	
% 文章标题：“流域尺度的水资源利用体系：过渡框架和发展困局”
\title{Regime transition identification for water utilization in river basin developments}

@@

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{
	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.
	Water, a key resource to support the sustainable development of human societies, whose natural cycle has been modified by growing socio-economic processes. We propose a new method with an integrated index to detect water utilization regimes and applying it to the Yellow River Basin, a typical overexploited basin in China. After sketching changes of relationships between social development and water utilization within the Yellow River Basin, we summarized a general transition framework. By predicting widespread development dilemmas, it can be a useful guideline for basins all around the world in their sustainable developing trajectories. 
}

@@

%tag 摘要
\begin{abstract}
	For water utilization as blood that sustains social developments, humans have harnessed basins, modified river cycles and triggered a range of regime shifts all around the world.
	Here, considering three important dimensions of water utilization (stress, priority and configuration), we develop an Integrated Water Resources Utilization (IWRU) Index at a basin scale to indicate regime shifts. 
	By applying this index to the Yellow River Basin, China, our results suggest there were two regime shifts over half a century, whose drivers were economic growths, managements and efficiency improvement.
	Differ from previous onefold descriptions, IWRU captures various considerations intertwined in water utilization, based on which we proposed a transition framework of relationships associated regime shifts with developments.
	By predicting widespread development dilemmas in transition regimes of water utilization, it can be a useful guideline for big river basins to develop in a coordinated way.
\end{abstract}

@@

% tag 引言第一段
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for myriad Earth system processes, but also supporting development of human societies in various aspects. 
% TODO 这里增加三篇“大文章”参引
% 但同时, 人类的改造也深刻影响了自然水循环过程, 相关变化可能影响人水系统功能的不利转变，并带来发展困局。
However, human's modification has profoundly influenced the water cycle which may lead adverse changes to functions of human-water systems, resulting in development dilemmas \cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% TODO 这里增加参考文献，人类对水循环的改造 
% 大河流域常是经济和文明发展的中心，同时也是面临人类世压力挑战的主要地区，亟需综合水资源治理以实现可持续发展。
Facing major challenges in the Anthropocene, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need for integrated water resources management toward sustainability \cite{bestAnthropogenicStressesWorld2019}. 
% 因此理解人类社会发展与水资源利用的复杂关系，对此有帮助。
Therefore, understanding the complex relationship between human societies, water resources utilization and their transitions provides underlying supports for developing in a coordinated and sustainable way at a basin scales.

@@

% %tag 结果2
% \subsection*{Differences between water utilization regimes}
% % 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
% The differences between the water utilization regimes are reflected in changes of all three dimensions.

% % 从阶段一到阶段二，水资源压力的变化最为明显
% Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D and \textit{SI Appendix} Method S4).   
% % 1. 水资源丰富，耗水量少且灵活用水
% In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig. S3) and most of which were flexible water utilization (\textit{SI Appendix} Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix} Fig. S5). As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.

% % 另一方面，P2-P3，持续变化的水资源利用倾向与格局
% On the other hand, as the most positive contributors to the IWRU index in P2 and P3 separately, priority (Figure~\ref{fig:dimensions}B) and configuration (Figure~\ref{fig:dimensions}C) of water utilization were keeping to enlarge their impacts. 
% % 首先是用水比例的变化
% Representing priority of water utilization, increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, while their influences are weakening (Figure~\ref{fig:dimensions}E).
% % 再讨论用水格局的变化
% However, configuration of water utilization, whose contributions to the IWRU are increasing, were mainly benefited from decreasing differences in the amount of water resources used, both intersectoral and regional (Figure~\ref{fig:dimensions}F).

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Drivers of water utilization regime shifts: economy growths, efficiency changes, and management practices.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Constructions' finished time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and storage. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
	}
	\label{fig:Causes}
\end{figure}

@@

\subsection*{Shifted regimes with development}
% 我们发明的指数能将三个维度的变化捕捉到。
The IWRU index captures, with three dimensions (stress, priority and configuration), the complex human-water feedbacks that links social development and water resources utilization. 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig. S8). 
% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development then.
% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure (\textit{SI Appendix} Table S2), and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C). 
% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
As a result, this regime is characterized by a rapid expansion of irrigation water to support development of agriculture.

% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff. In 1972, the Yellow River was cut off for the first time with a length of 310 km for 19 days, and continued to be cut off for many years since then (\textit{SI Appendix} Fig. S9). 
% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
Came to the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
Since then, the expansion trend of agriculture has been constrained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market. In addition, most laws and regulations have been successively implemented (\textit{SI Appendix} Table 2). For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.

@@

\subsection*{Regime transition framework}

\begin{figure*}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		Transition framework of the water utilization regime towards nature-society dualistic water cycle.
		\textbf{A. Natural cycle:} As an indispensable provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic cycle, water resource plays a non-provisioning role. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional cycle:} Entering this phase, with further developed and economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:summary}
\end{figure*}

@@

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% 资源陷阱和失配，导致崩溃
Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
\cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% 转型应对陷阱
A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (Figure~\ref{fig:traps}).
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
In the YRB as an example, after the successive exploitation of agriculture (from P1 to P2, refers from natural cycle to a local cycle), industry and services, the water resource extraction rate has reached $79\%$, far exceeding the internationally recognized warning threshold of $40\%$. The resource dilemma revealed after the regime shift, with severe runoff outages and groundwater depletion of the Yellow River (\textit{SI Appendix} Fig. S8).
% 后来摆脱了资源陷阱（表现形式 xxx）。
To get rid of the resource dilemma, a clear transformation towards integrated basin management proposed, with several management practices. 
% 一段有关87分水方案的介绍
The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}. Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}. 
These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
% 资源困局可能普遍存在
Since similar phenomena occurred in Mississippi and Indus River Basins, the fact that the accelerated development has been followed by water scarcity and a series of ecological problems shows that the resource dilemmas is pervasive in the transition trajectory, especially from natural cycle to regional cycle 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}.
% 通过协同治理来摆脱困局也普遍存在
Similarly, many of the world's major river basins have eventually moved towards a system of integrated governance, especially for trans-boundary rivers (e.g. Danube and Mekong River), where water resources are in need of collaborative governance \cite{bodinCollaborativeEnvironmentalGovernance2017,unep-dhiTransboundaryRiverBasins2016}.

### 2020-10-09 tex/sup/supplementary_information.tex
change abstract and title

@@

% %% 表格
% \begin{table}\centering
% \caption{This is a table}

% % 表格
% \begin{tabular}{lrrrr}
% Species & CBS & CV & G3 \\
% \midrule
% 1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
% 2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
% 3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
% \bottomrule
% \end{tabular}
% \end{table}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regimes and their main contributors.
		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		}
	\label{fig:dimensions}
\end{figure}

@@

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
	\caption{
		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure. Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
	}
	\label{fig:traps}
\end{figure}
